%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Leminda AI} % Organization
    {Binyamina, Israel} % Location
    {Sept. 2022 - May. 2024} % Date(s)
    {
       \begin{cvitems}
          \item {Developed a fully automated system using TS, Puppeteer and Express that scans websites, identifies fake images by analyzing accompanying text, and uses Large Language
Models (LLMs) and OpenAI to streamline the tagging process. This system stored all the processed data in SQL databases, creating a robust
database for training language models to enhance fake image detection.}
          \item {Developed and maintained a Chrome extension using JavaScript and React, directly integrating with Twitter to enhance user interactions.}
          \item {Developed and optimized REST APIs with Python,MongoDB,and SWC-DB.}
          \item {Worked with React,HTML,and Tailwind CSS to create a user-friendly interface.}
          \item {Collaborated with cross-functional teams to design, develop, and deploy software solutions, following Agile methodologies to maintain a steady
workflow and iterative improvement.}
          \item {Worked under both Linux and Windows environments. Maintained all codebases using Git for version control, ensuring efficient and reliable
source code management across project.}
          \item {Developed and maintained automation infrastructure and tests from scratch for AWS cloud-based web applications using Cypress.}
          \item {Investigation of software issues resulting from testing.}
          \item {Implemented continuous integration and continuous deployment (CI/CD) processes for automation testing.}
        \end{cvitems}
    }

%-------------------------------------------------------
  \cventry
    {QA Engineer and Integration} % Job title
    {Elbit Systems(El-Op)} % Organization
    {Rehovot, Israel} % Location
    {May. 2019 - Sept. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
         \item {Conducted full inspections of complex systems, environmental testing, final ATP, systems calibration, and calibration testing.}
         \item {Created and maintained ATP / ESS / STD / STR documents.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

